\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-03 paper.tex
monetization section

@@

Over the course of the project, we had to develop multiple applications in
different languages. In total, we opened five different repositories: the blog,
the \LaTeX source code for our paper, the Arduino code for the heart project,
and of course one for Editour and another for ARuko. These five repositories
span across multiple different markup and programming languages, including C\#,
C++, JavaScript, HTML, CSS (and the \LaTeX markup language used to typeset this
paper.) This gave us a welcome amount of practice using git for version control,
as well as GitHub's other features oriented around coordinating a team.

All three members of the team were contributing code and updating assets such as
graphics and sound. Code complexity grew quickly as more features were added
across the entire software stack. GitHub and git enabled us to view the history
of the code and revert back to working versions when absolutely necessary. We
researched the proper methodology of using version control in a small team,
applying this methodology as best we could. This enabled us to work together
efficiently, track down bugs, undo mistakes, and sometimes review each other's
code for quality when time allowed.

@@

Creating ``pull requests'' through the GitHub web interface has a few advantages
over directly merging code using git. Firstly, the pull request feature
integrates with ``Issues'' page very well. By typing `resolves' along with the
number associated with an issue into the description of a pull request, GitHub
will automatically close the issue when the pull request is approved. This is
not only remarkably convenient, but also self-documenting since the descriptions
of pull requests would contain the issues they were resolving. Secondly,
creating a pull request allows code to be reviewed by other members of the team
very easily. Reviewers can view the entire diff and add comments line-by-line.
Other collaborators can easily respond to those comments. Reviewers can also
request certain features be changed before the branch is merged, which allowed
us to enforce that issues with the code were actually addressed.
% TODO explain what the heck a diff is

>>>>

\subsection{Monetization for ARuko}
\label{sec:monetizationForAruko}

Partway through our project, Atticus Sims let us know that he was looking to
monetize the app we were developing for him. He also informed us that the IQP
team would be looking for funding options in order to ``bootstrap'' the project.
One monetization method he proposed was potentially marketing the app to hotels,
allowing hotels to sell tours for download through in-app purchases.

In order to get an app approved for the App Store or the Google Play store,
there is sometimes a lengthy approval process. This might have been possible if
our project had been more prescriptive from the start.

We did perform some preliminary research about the monetization models Atticus
proposed and brought forth some potential roadblocks regarding each one. We let
Atticus know that we had logistical concerns about circumventing Apple's or
Google's in-app purchases by locking content behind a different payment process.
Additionally, we informed Atticus that he would have to purchase a commercial
Vuforia license in order to deploy the app onto any
storefront~\autocite{vuforialicense2018}, which Atticus was not willing to do at
the time. The free version of Vuforia comes branded with a watermark in the
bottom left corner.\footnote{The final design of our app incidentally covers up
the watermark with our own UI elements. This does not change the fact that we
would not be able to deploy the app without a proper commercial license for
Vuforia.}

Our concerns about focusing on monetization for Kyoto~VR were twofold. Firstly,
we were worried that this kind of work strayed too far away from the academic
intent of the project---the intent being to explore various ways in which AR and
geolocation could be used in tandem to create an improved experience for
tourists. For our purposes, the app was meant to demonstrate our discoveries in
the form of a polished prototype. While we feel as though we achieved this goal,
we made certain compromises in the way of experimentation in order to leave
Kyoto~VR with a potentially marketable product. We made it clear to Atticus that
deploying our app on the Google Play Store or App Store would not be within the
scope of our academic project as per our advisers' advice.

@@

Over the course of the project, we had to develop multiple applications in
different languages. In total, we opened five different repositories: the blog,
the \LaTeX~source code for our paper, the Arduino code for the heart project,
and of course one for Editour and another for ARuko. These five repositories
span across multiple different markup and programming languages, including C\#,
C++, JavaScript, HTML, CSS (and the \LaTeX~markup language used to typeset this
paper.) This gave us a welcome amount of practice using Git for version control,
as well as GitHub's other features oriented around coordinating a team.

All three members of the team were contributing code and updating assets such as
graphics and sound. Code complexity grew quickly as more features were added
across the entire software stack. GitHub and Git enabled us to view the history
of the code and revert back to working versions when absolutely necessary. We
researched the proper methodology of using version control in a small team,
applying this methodology as best we could. This enabled us to work together
efficiently, track down bugs, undo mistakes, and sometimes review each other's
code for quality when time allowed.

@@

Creating ``pull requests'' through the GitHub web interface has a few advantages
over directly merging code using Git. Firstly, the pull request feature
integrates with ``Issues'' page very well. By typing `resolves' along with the
number associated with an issue into the description of a pull request, GitHub
will automatically close the issue when the pull request is approved. This is
not only remarkably convenient, but also self-documenting since the descriptions
of pull requests would contain the issues they were resolving. Secondly,
creating a pull request allows code to be reviewed by other members of the team
very easily. Reviewers can view the entire diff and add comments line-by-line.
Other collaborators can easily respond to those comments. Reviewers can also
request certain features be changed before the branch is merged, which allowed
us to enforce that issues with the code were actually addressed.
% TODO explain what the heck a diff is
